\section*{Author Revision Action Plan for TIFS Submission}

\subsection*{Purpose of This Revision Plan}
This revision plan converts the reviewer-style critiques into an \textbf{author-side implementation checklist}. The goal is not merely to polish wording, but to make the manuscript technically self-consistent, more focused, more reproducible, and better aligned with the standards of IEEE Transactions on Information Forensics and Security (TIFS).

The current manuscript has a \textbf{promising topic} but still suffers from four structural weaknesses:
\begin{enumerate}
    \item the paper currently tries to do too many things at once;
    \item the theoretical assumptions are not fully self-consistent;
    \item the mechanism definition is incomplete for a security journal;
    \item the experiments do not yet fully validate the main security claims.
\end{enumerate}
Accordingly, the revision must proceed in the order:
\[
\text{soundness} \rightarrow \text{mechanism completeness} \rightarrow \text{focus} \rightarrow \text{evaluation} \rightarrow \text{editorial cleanup}.
\]

\subsection*{Part I. Top-Level Revision Strategy}

\subsubsection*{A1. Decide the true center of the paper}
Before editing any section, decide what the paper is \textbf{really about}. The current draft mixes:
\begin{itemize}
    \item entropy sensitivity analysis,
    \item histogram DP release,
    \item synthetic-data release mechanism \(F\),
    \item Wiener kernel / RKHS mean release,
    \item image utility plots,
    \item Noisy-SGD discussion.
\end{itemize}
This is too broad for a sharp TIFS paper.

\paragraph{Author action.}
Choose \textbf{one primary contribution line} and demote the rest to supporting or supplementary roles.

\paragraph{Recommended choice.}
The strongest candidate is:
\begin{quote}
\textbf{A formally analyzed entropy-calibrated differentially private data release framework, with a complete mechanism definition and attack-based security evaluation.}
\end{quote}

\paragraph{What this means concretely.}
\begin{itemize}
    \item Keep entropy sensitivity as a theoretical foundation.
    \item Keep mechanism \(F\) as the main release mechanism \emph{if} it can be fully specified and its theorem repaired.
    \item Keep RKHS / Wiener material only if it is truly an instance of the same framework.
    \item Remove, shorten, or move image-only utility discussion unless it directly instantiates the same mechanism.
    \item Reduce Noisy-SGD to a brief remark or delete it unless it becomes part of the central theorem/experiment story.
\end{itemize}

\subsubsection*{A2. Rebuild the manuscript around one pipeline}
The final paper should follow this exact logic:
\[
\text{Threat Model}
\rightarrow
\text{Mechanism Definition}
\rightarrow
\text{Privacy Theorem}
\rightarrow
\text{Utility / Sensitivity Analysis}
\rightarrow
\text{Attack Evaluation}.
\]

\paragraph{Author action.}
Every section must serve this pipeline. If a section does not directly support one of these five stages, either shorten it drastically, move it to the appendix, or remove it.

\subsection*{Part II. Highest-Priority Technical Repairs}

\subsubsection*{B1. Fix the adjacency definition globally}
This is the first issue that must be repaired because it affects theorem validity.

\paragraph{Problem.}
The manuscript text says add/remove adjacency, but the proof of the entropy theorem is written as if both adjacent datasets have the same size \(n\), which is a replacement/substitution model.

\paragraph{Author action.}
Choose \textbf{one and only one} adjacency definition:

\paragraph{Option 1: add/remove adjacency}
\[
D \sim D' \iff D' = D \cup \{x\} \text{ or } D = D' \cup \{x\}.
\]
Then:
\[
|D'| = |D| \pm 1.
\]

\paragraph{Option 2: replacement adjacency}
\[
D \sim D' \iff |D|=|D'|=n,\quad |\{i:x_i \neq x_i'\}|=1.
\]

\paragraph{Recommended author choice.}
If your entropy proof is easier to salvage under fixed dataset size, use \textbf{replacement adjacency}. This will likely make the theorem cleaner and easier to defend. However, if the synthetic mechanism theorem truly depends on add/remove adjacency, then the entropy proof must be rewritten accordingly.

\paragraph{Required edits.}
Once the choice is made:
\begin{enumerate}
    \item revise the preliminaries;
    \item revise Definition 1;
    \item revise the entropy theorem statement;
    \item revise the theorem proof in the appendix;
    \item revise all later mechanisms and discussions that invoke adjacency.
\end{enumerate}

\paragraph{Non-negotiable rule.}
The final manuscript must never mix the two adjacency models implicitly.

\subsubsection*{B2. Rewrite the entropy sensitivity theorem with explicit assumptions}
\paragraph{Problem.}
The current theorem statement and proof do not cleanly expose the exact assumptions used.

\paragraph{Author action.}
State the theorem in a theorem-ready form such as:
\[
\Delta_H
=
\max_{D \sim D'}
\left|
H(D)-H(D')
\right|,
\]
where
\[
H(D) = -\sum_{i=1}^{m} p_i \log_2 p_i,
\qquad
p_i = \frac{c_i}{|D|}.
\]

Then explicitly define:
\begin{itemize}
    \item what \(m\) is,
    \item what the histogram bins are,
    \item whether zero-probability terms are omitted or handled by continuity,
    \item which adjacency relation is used.
\end{itemize}

\paragraph{Additional author strengthening.}
Do not stop at a symbolic upper bound. Add an empirical tightness study:
\[
r(n,m)=\frac{\widehat{\Delta H}}{\Delta_H^{\mathrm{bound}}}.
\]
This will help show that the theorem is not merely formal, but also informative.

\subsubsection*{B3. Repair the synthetic-mechanism DP theorem}
\paragraph{Problem.}
The current proof conditions involving \(k,t,\gamma,\varepsilon_0\) appear inconsistent with the actual experimental settings.

\paragraph{Author action.}
You must do a full theorem audit.

\paragraph{Practical revision workflow.}
\begin{enumerate}
    \item Copy the theorem and proof into a separate working document.
    \item List all assumptions used explicitly or implicitly.
    \item For every inequality, annotate the condition required for it to hold.
    \item Compare those conditions against the actual experiment parameters.
    \item Remove any proof line that depends on a parameter regime not used experimentally.
\end{enumerate}

\paragraph{What the final theorem should look like.}
Instead of a vague theorem, write:
\[
\text{Mechanism } F \text{ is } (\varepsilon,\delta)\text{-DP provided } 
(\varepsilon_0,\gamma,t,k)\in\mathcal{A},
\]
where \(\mathcal{A}\) is an explicitly defined admissible set.

\paragraph{Why this matters.}
A TIFS reviewer will immediately question any theorem whose proof uses a regime that the experiments violate. This is one of the most likely desk-rejection / reject triggers in the current draft.

\subsubsection*{B4. Fully specify the mechanism \(F\)}
\paragraph{Problem.}
The current manuscript gives the idea of the mechanism, but not yet a fully auditable security-journal specification.

\paragraph{Author action.}
Replace high-level prose by a complete algorithmic definition.

\paragraph{Minimum required form.}
The main paper should specify:
\begin{align}
&\textbf{Input: } D,\varepsilon,\delta,\varepsilon_0,k,t,\gamma,\rho, \\
&\textbf{Seed selection: } s \sim \mathrm{Unif}(D), \\
&\textbf{Candidate generation: } y \sim p_s(\cdot), \\
&\textbf{Partition identification: } j = I_s(y), \\
&\textbf{Acceptance test: } \mathcal{A}(D,s,y)=\mathbf{1}\{L \ge k-|C_j(D,y)|\}, \\
&\textbf{Output rule: } F(D)=y \text{ if accepted, else resample.}
\end{align}

\paragraph{You must define explicitly:}
\begin{itemize}
    \item the universe \(U\),
    \item the support of \(y\),
    \item the exact distribution \(p_s(y)\),
    \item the rule \(I_s(y)\),
    \item the law of \(L\),
    \item whether there is a maximum number of resampling attempts,
    \item what happens when repeated rejection occurs.
\end{itemize}

\paragraph{Additional author action.}
Also include:
\begin{itemize}
    \item algorithm pseudocode,
    \item runtime discussion,
    \item parameter meaning table,
    \item implementation notes sufficient for reproduction.
\end{itemize}

\subsection*{Part III. Manuscript Restructuring by Section}

\subsubsection*{C1. Title}
\paragraph{Problem.}
The current title is overloaded and likely overstates the operational role of Renyi entropy.

\paragraph{Author action.}
Either:
\begin{enumerate}
    \item make Renyi entropy central in the method and experiments; or
    \item remove it from the title.
\end{enumerate}

\paragraph{Recommended author strategy.}
Unless you add new experiments showing how \(\alpha\) changes calibration or risk, it is safer to \textbf{remove Renyi entropy from the title} and keep it as an appendix or secondary theorem.

\paragraph{Possible title style.}
\begin{quote}
\textbf{Entropy-Calibrated Differentially Private Data Release with Formal Guarantees and Attack-Based Evaluation}
\end{quote}

\subsubsection*{C2. Abstract}
\paragraph{Problem.}
The abstract currently tries to summarize too many contributions at once.

\paragraph{Author action.}
Rewrite the abstract into exactly five sentences:
\begin{enumerate}
    \item problem and threat model;
    \item proposed mechanism;
    \item main theorem;
    \item evaluation protocol;
    \item main result and significance.
\end{enumerate}

\paragraph{Recommended rewrite logic.}
Do not list several semi-independent innovations. Instead present one coherent story:
\begin{quote}
We study \(\cdots\); we propose \(\cdots\); we prove \(\cdots\); we evaluate under \(\cdots\); results show \(\cdots\).
\end{quote}

\subsubsection*{C3. Introduction}
\paragraph{Problem.}
The introduction currently opens too many fronts.

\paragraph{Author action.}
Rewrite the introduction around one core question:
\begin{quote}
How can we design a differentially private release mechanism whose sensitivity is formally controlled, whose algorithm is completely specified, and whose security is validated against inference attacks?
\end{quote}

\paragraph{Required introduction structure.}
\begin{enumerate}
    \item motivate the privacy/security problem;
    \item explain why standard release is risky;
    \item identify the gap in existing methods;
    \item state your mechanism and theorem;
    \item list contributions that map one-to-one to later sections.
\end{enumerate}

\paragraph{Important author rule.}
Every contribution listed in the introduction must later appear in:
\begin{itemize}
    \item a dedicated method subsection,
    \item a theorem or formal proposition,
    \item and an experiment or analysis.
\end{itemize}

\subsubsection*{C4. Related Work}
\paragraph{Problem.}
The related work is too broad and not competitive enough for TIFS.

\paragraph{Author action.}
Split related work into four focused blocks:
\begin{enumerate}
    \item DP data release / synthetic data release;
    \item entropy-based privacy or sensitivity analysis;
    \item RKHS or function-space privacy methods;
    \item attack-based privacy auditing.
\end{enumerate}

\paragraph{Required addition.}
Add a comparison table:
\[
\begin{array}{l|c|c|c|c|c}
\text{Method} & \text{Release type} & \text{Formal DP} & \text{Entropy role} & \text{Attack eval.} & \text{Difference}\\
\hline
\text{Prior 1} & & & & & \\
\text{Prior 2} & & & & & \\
\text{This work} & & & & &
\end{array}
\]

\paragraph{Author target.}
The reader should understand in one page:
\begin{quote}
What is closest to this paper, and exactly what is different here?
\end{quote}

\subsubsection*{C5. Threat Model}
\paragraph{Problem.}
Threats are discussed somewhat broadly, but only some are actually evaluated.

\paragraph{Author action.}
Separate the threats formally:
\begin{align}
&\text{Membership inference: determine whether } x \in D, \\
&\text{Attribute inference: infer hidden sensitive attributes}, \\
&\text{Record linkage: match released samples to known identities}.
\end{align}

\paragraph{Required clarification.}
Explicitly state:
\begin{itemize}
    \item which threat is formally bounded by DP;
    \item which threat is directly evaluated in experiments;
    \item which threat remains future work.
\end{itemize}

\paragraph{Recommended author choice.}
If only MIA is truly evaluated now, then narrow the claims and do not implicitly claim complete defense against all inference attacks.

\subsubsection*{C6. Preliminaries and Notation}
\paragraph{Problem.}
This section currently does not fully protect the later theory from ambiguity.

\paragraph{Author action.}
Add a notation table including:
\[
D,\ D',\ n,\ m,\ c_i,\ p_i,\ H,\ H_\alpha,\ \varepsilon,\ \delta,\ \varepsilon_0,\ k,\ t,\ \gamma,\ \rho,\ F,\ U.
\]

\paragraph{Additional action.}
Define every mechanism domain and codomain before theorems begin. This will reduce proof ambiguity and improve reviewer confidence.

\subsubsection*{C7. Entropy Theorem Section}
\paragraph{Problem.}
The result may be useful, but it needs a cleaner presentation.

\paragraph{Author action.}
Organize the section as:
\begin{enumerate}
    \item setup and histogram model;
    \item theorem statement;
    \item interpretation;
    \item proof deferred to appendix;
    \item numerical tightness study.
\end{enumerate}

\paragraph{Recommended improvement.}
Add one paragraph explicitly explaining why entropy sensitivity matters operationally for your release mechanism.

\subsubsection*{C8. Renyi Entropy Section}
\paragraph{Problem.}
At present this section is mathematically interesting but operationally weak.

\paragraph{Author action.}
Choose one of the following:
\begin{itemize}
    \item \textbf{Strong option:} add experiments varying \(\alpha\) and show what Renyi sensitivity contributes in practice;
    \item \textbf{Safe option:} shorten the section and move most details to the appendix.
\end{itemize}

\paragraph{Recommended author choice.}
If time is limited, use the safe option. Keep the result, but do not let it dominate the title or abstract.

\subsubsection*{C9. Mechanism Section}
\paragraph{Problem.}
This section should be the heart of the paper, but currently reads more like a sketch.

\paragraph{Author action.}
Turn it into a complete method section with:
\begin{itemize}
    \item intuitive overview,
    \item formal definition,
    \item algorithm box,
    \item parameter table,
    \item theorem pointer,
    \item practical implementation note.
\end{itemize}

\paragraph{Author note.}
This is the section that most directly determines whether TIFS reviewers perceive the work as serious and reproducible.

\subsubsection*{C10. RKHS / Wiener Section}
\paragraph{Problem.}
This material is mathematically interesting but currently insufficiently integrated.

\paragraph{Author action.}
Decide whether this section is:
\begin{enumerate}
    \item the main instantiation of the mechanism; or
    \item a secondary example.
\end{enumerate}

\paragraph{If it is main.}
You must explain:
\begin{itemize}
    \item why RKHS is needed,
    \item how it changes the mechanism,
    \item how \(\rho\) affects privacy and utility,
    \item how the experiments directly validate this part.
\end{itemize}

\paragraph{If it is secondary.}
Move most of it to the appendix or supplementary material.

\subsubsection*{C11. Noisy-SGD Material}
\paragraph{Problem.}
This currently weakens focus.

\paragraph{Author action.}
Unless Noisy-SGD is directly used in the mechanism or experiments, remove it from the main contribution narrative.

\paragraph{Recommended author choice.}
Reduce it to one short paragraph in discussion/future work.

\subsection*{Part IV. Experimental Revision Plan}

\subsubsection*{D1. Reorganize the experimental section}
\paragraph{Author action.}
Split experiments into three blocks:
\begin{enumerate}
    \item \textbf{Bound / theorem validation},
    \item \textbf{Utility evaluation},
    \item \textbf{Security attack evaluation}.
\end{enumerate}

\paragraph{Why.}
This makes the experimental logic match the paper logic:
\[
\text{theorem} \rightarrow \text{usefulness} \rightarrow \text{security}.
\]

\subsubsection*{D2. Add theorem-aligned empirical validation}
\paragraph{Author action.}
Add experiments that directly test the key theoretical claims.

\paragraph{For entropy theorem.}
Estimate
\[
\widehat{\Delta H}
=
\max_{D \sim D'} |H(D)-H(D')|
\]
on controlled synthetic examples and compare it against the bound.

\paragraph{For mechanism theorem.}
Estimate empirical privacy loss:
\[
L(o)=\log\frac{\Pr[F(D)=o]}{\Pr[F(D')=o]}.
\]
Then show whether the empirical distribution is compatible with the claimed \((\varepsilon,\delta)\) guarantee.

\paragraph{This is highly recommended.}
It will substantially strengthen the paper because it closes the loop between theorem and experiment.

\subsubsection*{D3. Strengthen attack evaluation}
\paragraph{Problem.}
Current attack evaluation is too weak for TIFS.

\paragraph{Author action.}
For MIA, explicitly define:
\begin{align}
& o \leftarrow F(D) \text{ or } F(D'), \\
& a(o) \in \mathbb{R}, \\
& \hat{b}=\mathbf{1}\{a(o)\ge \tau\}.
\end{align}

Then report:
\begin{itemize}
    \item attack accuracy,
    \item balanced accuracy,
    \item ROC-AUC,
    \item confidence intervals,
    \item standard deviation across repeated runs.
\end{itemize}

\paragraph{Add stronger baselines.}
At minimum:
\begin{itemize}
    \item a threshold attack,
    \item a nearest-neighbor / linkage attack,
    \item a stronger task-specific inference attack if possible.
\end{itemize}

\subsubsection*{D4. Strengthen utility metrics}
\paragraph{Problem.}
Some current metrics are too indirect.

\paragraph{Author action.}
Prioritize metrics that align directly with your release goal:
\begin{align}
&\mathrm{MAE}_{\mathrm{count}}, \\
&|H_{\mathrm{orig}}-H_{\mathrm{priv}}|, \\
&D_{\mathrm{KL}}(p\|\tilde p), \\
&\mathrm{TV}(p,\tilde p), \\
&\text{downstream accuracy}, \\
&\text{linkage success rate}, \\
&\text{attribute inference accuracy}.
\end{align}

\paragraph{Recommended author choice.}
If the paper is mainly about general DP release rather than image-specific release, move PSNR/SSIM/MAE image plots to a secondary or supplementary position.

\subsubsection*{D5. Improve baselines}
\paragraph{Problem.}
Laplace and Gaussian alone are not enough.

\paragraph{Author action.}
Add baselines from the nearest relevant literature:
\begin{itemize}
    \item standard DP histogram release,
    \item exponential mechanism if relevant,
    \item DP synthetic release methods,
    \item kernel-based privatization baselines if RKHS remains central.
\end{itemize}

\paragraph{Author note.}
You do not necessarily need many baselines, but you do need the \textbf{right} baselines.

\subsection*{Part V. Writing and Presentation Repairs}

\subsubsection*{E1. Unify theorem numbering and contribution mapping}
\paragraph{Problem.}
The theorem numbering and contribution mapping are currently inconsistent across materials.

\paragraph{Author action.}
Perform a full consistency check:
\begin{enumerate}
    \item title,
    \item abstract,
    \item introduction contributions,
    \item theorem numbering,
    \item appendix numbering,
    \item conclusion claims.
\end{enumerate}

\paragraph{Non-negotiable rule.}
Every theorem mentioned in the introduction must exist in the main text with the same numbering and same role.

\subsubsection*{E2. Remove overclaims}
\paragraph{Problem.}
Some claims currently sound broader than the evidence supports.

\paragraph{Author action.}
Tone down claims such as:
\begin{itemize}
    \item broad protection against all inference attacks,
    \item strong practical superiority without enough baselines,
    \item centrality of Renyi entropy if it remains auxiliary,
    \item unified framework if the paper remains multi-threaded.
\end{itemize}

\subsubsection*{E3. Improve figure logic}
\paragraph{Author action.}
Reorder figures so they support one argument sequence:
\begin{enumerate}
    \item theorem intuition / bound figure,
    \item mechanism diagram,
    \item utility tradeoff figure,
    \item attack evaluation figure.
\end{enumerate}

\paragraph{For each figure, answer in the caption:}
\begin{itemize}
    \item what claim does this support?
    \item does it validate theory, utility, or security?
    \item why is this metric relevant?
\end{itemize}

\subsubsection*{E4. Rewrite the conclusion conservatively}
\paragraph{Author action.}
The conclusion should reflect only what has been formally shown and empirically supported.

\paragraph{Recommended conclusion logic.}
\begin{enumerate}
    \item restate the problem;
    \item restate the mechanism;
    \item summarize the formal guarantee;
    \item summarize the strongest experimental findings;
    \item state limitations honestly;
    \item suggest future work.
\end{enumerate}

\subsection*{Part VI. Appendix Repair Plan}

\subsubsection*{F1. Rewrite the appendix after the main paper is stabilized}
\paragraph{Author action.}
Do \textbf{not} try to patch the appendix before you finalize:
\begin{itemize}
    \item adjacency,
    \item theorem statements,
    \item parameter assumptions.
\end{itemize}

\paragraph{Reason.}
At the moment, the appendix exposes the inconsistencies rather than resolving them.

\subsubsection*{F2. Use a proof architecture}
\paragraph{Author action.}
Rewrite proofs as:
\begin{enumerate}
    \item assumptions;
    \item lemma;
    \item intermediate bound;
    \item theorem conclusion;
    \item interpretation.
\end{enumerate}

\paragraph{Recommended proof style.}
Avoid compressed proof jumps. TIFS reviewers respond much better to explicit proof scaffolding than to elegant but fragile shortcuts.

\subsection*{Part VII. Priority-Ordered Execution Checklist}

\subsubsection*{Priority 1: Soundness}
\begin{enumerate}
    \item Fix adjacency globally.
    \item Rewrite the entropy theorem accordingly.
    \item Repair the synthetic DP theorem so assumptions match experiments.
\end{enumerate}

\subsubsection*{Priority 2: Mechanism completeness}
\begin{enumerate}
    \item Fully define \(F\).
    \item Add complete pseudocode and parameter table.
    \item Clarify rejection/resampling/runtime behavior.
\end{enumerate}

\subsubsection*{Priority 3: Contribution focus}
\begin{enumerate}
    \item Choose the central contribution.
    \item Reduce side stories.
    \item Demote weakly integrated material.
\end{enumerate}

\subsubsection*{Priority 4: Experimental credibility}
\begin{enumerate}
    \item Add theorem-aligned validation.
    \item Strengthen MIA and add stronger attack baselines.
    \item Improve utility metrics and comparison baselines.
\end{enumerate}

\subsubsection*{Priority 5: Editorial cleanup}
\begin{enumerate}
    \item Fix title/abstract/introduction alignment.
    \item Fix numbering and notation.
    \item Remove overclaims.
    \item Rewrite conclusion conservatively.
\end{enumerate}

\subsection*{Part VIII. Final Author Guidance}
The manuscript does not currently fail because the topic is weak. It fails because the current version does not yet present one technically consolidated paper. The most effective revision strategy is therefore \textbf{not} to add more content everywhere, but to:
\begin{enumerate}
    \item reduce scope,
    \item repair theorem soundness,
    \item fully define the mechanism,
    \item rebuild experiments around the central security claim.
\end{enumerate}

If these four goals are achieved, the paper will be substantially stronger and much closer to TIFS expectations.